Efficiently Handling Guards in the low level design of RPython's tracing JIT

### 2012-07-20 talk/vmil2012/paper.tex
typos

Guards interact with optimizations in various ways.
Most importantly optimizations try to remove as many operations
and therefore guards as possible.
This is done with many classical compiler optimizations.
In particular guards can be remove by subexpression elimination.
If the same guard is encountered a second time in the trace,
the second one can be removed.
This also works if a later guard is weaker implied by a earlier guard.

@@

Adding this additional information is done as follows.
So far, every variable in the symbolic frames
contains a constant or an SSA variable.
After allocation removal the variables in the symbolic frames can also contain
``virtual'' objects.
These are objects that were not allocated so far,
because the optimizer removed their allocation.
The virtual objects in the symbolic frames describe exactly
how the heap objects that have to be allocated on guard failure look like.
To this end, the content of the every field of the virtual object is described
in the same way that the local variables of symbolic frames are described.
The fields of the virtual objects can therefore be SSA variables, constants
or other virtual objects.
They are encoded using the same compact two-byte representation
as local variables.

>>>>

Guards interact with optimizations in various ways.
Most importantly optimizations try to remove as many operations
and therefore guards as possible.
This is done with many classical compiler optimizations.
In particular guards can be removed by subexpression elimination.
If the same guard is encountered a second time in the trace,
the second one can be removed.
This also works if a later guard is weaker implied by a earlier guard.

@@

Adding this additional information is done as follows.
So far, every variable in the symbolic frames
contains a constant or an SSA variable.
After allocation removal the variables in the symbolic frames can also contain
``virtual'' objects.
These are objects that were not allocated so far,
because the optimizer removed their allocation.
The virtual objects in the symbolic frames describe exactly
how the heap objects that have to be allocated on guard failure look like.
To this end, the content of every field of the virtual object is described
in the same way that the local variables of symbolic frames are described.
The fields of the virtual objects can therefore be SSA variables, constants
or other virtual objects.
They are encoded using the same compact two-byte representation
as local variables.
